Analysis and Figures for Gallego et al, 2020

### 2020-08-27 Scripts/Manuscript.Main.Analysis.Rmd
I think this is done

saveRDS( file = here("Output","Temp.pH.grid.RDS"))

future.scenario %>% 
  write_rds(file = here("Output", "future.simulation.rds"))

@@

```{r}
all.sim.data <- simData.nocrazys  #to see simulation data

@@

SIMPER.clusters %>% 
  mutate(summary.simper = map(summary.simper,function(.x) bind_rows(.x[1:length(.x)], .id = "comparison") %>% rownames_to_column("taxa"))) %>% pull(summary.simper) %>% set_names(SIMPER.clusters$Area) %>% bind_rows(.id = "Area") %>% separate(taxa, into = c("taxa",NA), sep = "\\...") %>% 
  filter (p < 0.05) %>% 
  write_csv(here("Output","simper.all.csv"))

## Get the data for all  areas
 SIMPER.clusters %>%
   pull(summary.simper)-> list.of.simpers
names(list.of.simpers) <- paste(SIMPER.clusters$Area, SIMPER.clusters$Season, sep = "_")

@@

```{r}
expanded.future %>% 
  left_join(phylum.info) %>% 
  nest(-phylum) %>% 
  # ungroup() %>% 
  # filter (phylum %in%c("Dinophyceae", "Bacillariophyta")) %>% 
  mutate(suma = map (data,~.x %>% group_by(taxa,Area, Year) %>%
                       summarise(tot = sum(present)) %>%
                       ungroup() %>% 
                       pivot_wider(names_from = Year, values_from = tot) %>% 
                        group_by(taxa) %>% mutate(diff = `2017` - `2095`)
                     )) %>% 
  select(phylum, suma) %>% 
  unnest(suma) %>%
  group_by(phylum) %>% arrange(desc(abs(diff))) %>% 
  separate(taxa, into = c("family","genus", "species"), sep = "\\|", remove = F) %>%
  mutate(label = case_when((species == "NA" & genus == "NA") ~ paste0(family, " sp."),
                           species == "NA" ~  paste0(genus, " sp."),
                           TRUE            ~ species)) -> taxa.and.diff

taxa.and.diff %>%
  slice(1:5) %>%
  arrange(diff) %>% pull(taxa) -> ahorasi

taxa.and.diff %>% 
  slice(1:5) %>%
  arrange(diff) %>% pull(label) -> reorder.labels
```

@@

expanded.future %>% 
  filter(taxa %in% ahorasi) %>%
  separate(taxa, into = c("family","genus", "species"), sep = "\\|", remove = F) %>%
  mutate(label = case_when((species == "NA" & genus == "NA") ~ paste0(family, " sp."),
                           species == "NA" ~  paste0(genus, " sp."),
                           TRUE            ~ species))    %>%
  mutate(Area = as.character(Area)) %>%
  mutate(Area = case_when(Area == "SJI" ~ "San Juan Island",
                          TRUE          ~ Area)) %>%
  mutate(Year = fct_rev(as.factor(Year) )) %>% 
  nest(-phylum) -> input.for.left

input.for.left %>% 
  mutate( plot.by.taxa = map2 (data, phylum, ~ .x %>%
                                 ggplot(aes(x= present,
                                            y = fct_relevel(label,reorder.labels))) +
                                 scale_fill_brewer(name = "Year",  type = "qual", palette = 4, direction = 1,
                                                   breaks=c("2017","2095")) +
                                 labs (x = "Probability of presence",
                                       y = "") +
                                 facet_wrap(~Area) +
                                 theme_minimal() +
                                 theme(strip.text.y = element_text(angle = 0),
                                       axis.text.y = element_text(face = "italic"),
                                       legend.direction = "horizontal",
                                       legend.position  = "bottom",
                                       plot.title.position = "plot",
                                       plot.title = element_text(face = "bold",vjust =  -5 ),
                                       axis.title.x.top  = element_text(face = "bold",vjust = 3) ) +
                                 ggtitle(.y)  +
                                 scale_x_continuous(limits = c(0,1),position = "top") )) %>%
  pull(plot.by.taxa) %>% 
  set_names(input.for.left$phylum) -> fig3.left

map(fig3.left, function(x) x+ geom_boxplot(aes(fill = as.factor(Year)))) -> fig3.left

fig3.left["Dinophyceae"]
```

@@

  scale_color_brewer(name = "Year",  type = "qual", palette = 4, direction = -1, breaks=c("2017","2095")) +
  ggforce::geom_mark_hull(data = all.sims.for.projection %>%
                            ungroup() %>%
                            mutate(Area = as.character(Area)) %>% 
                            mutate(Area = case_when(Area == "SJI" ~ "San Juan Island",
                            TRUE          ~ Area)) %>%
                            filter (Year %in% c(2017, 2095)) ,
                          aes(x= TemperatureCelsius, y = pH_units, group= Year, color = as.factor(Year),label = as.factor(Year)),
                          expand = unit(0.5, "mm"),
                 label.margin = margin(1, 1, 1, 1, "mm"),
                 label.buffer = unit(0, "mm"),
                 con.cap = 0 ,
                 alpha = 0.5) +
     facet_grid(.~Area) +
  guides(color = "none") +
    labs (x = "Temperature",
          y= "pH") +
    theme_minimal()+
    theme(legend.position = "bottom",
          legend.key.width  = unit(2 ,"cm"),
          axis.title.x = element_text(face = "bold"),
          legend.direction = "horizontal") +
    scale_x_continuous(position = "top")
}
```

@@

fig3.right["Dinophyceae"]
fig3.right["Bacillariophyta"]

@@

Following reviewer's suggestions, we are limiting the information displayed in the main Figures to two of most important phyla for coastal ecosystems dinamics: Diatoms and Dinoflagellates.

```{r select some }

layout <- "
AA
AA
FF
EE
EE
GG
"

wrap_plots(A = fig3.left[["Dinophyceae"]] +   labs(tag = "A"),
           F = plot_spacer(),
           E = fig3.left[["Bacillariophyta"]] ,
           G = guide_area(),
            design = layout, heights = c(5,5,1,5,5,5), guides = "collect") -> left

layout2 <- "
#BB
#BB
JJJ
#HH
#HH
III
"
wrap_plots(B = fig3.right[["Dinophyceae"]] +   labs(tag = "B"),
           J = plot_spacer(),
           H = fig3.right[["Bacillariophyta"]] ,
           I = guide_area(),
            design = layout2,heights = c(5,5,1,5,5,5),
           widths = c(1,2,2), guides = "collect") -> right

(left|right)+plot_layout(widths = c(2,3))  -> plot 
   ggsave(plot , filename = here("Figures","Manuscript", paste0("Top_fig3_",Sys.Date(),".Other.sel.png")), units = "in", dpi = "retina", width = 20, height = 12)

@@

map2(fig3.left, fig3.right, 
     function(.x,.y){

@@

paths <- paste0("Supp.fig.",names(fig3.left),".png")

>>>>

write_rds( path  = here("Output","Temp.pH.grid.RDS"))

future.scenario %>% 
  write_rds(path = here("Output", "future.simulation.rds"))

@@

@@

## Get the data for all  areas
 SIMPER.clusters %>%
   pull(summary.simper)-> list.of.simpers
names(list.of.simpers) <- SIMPER.clusters$Area

@@

```{r choose taxa with more change}
expanded.future %>% 
  left_join(phylum.info) %>% 
  nest(-phylum) %>% 
  mutate(suma = map (data,~.x %>% group_by(taxa,Area, Year) %>%
                       summarise(prop = mean(present)) %>%
                       ungroup() %>% 
                       pivot_wider(names_from = Year, values_from = prop) %>% 
                        group_by(taxa) %>% mutate(diff = `2017` - `2095`) %>% 
                       pivot_wider(names_from = Area, values_from = c(`2017`, `2095`, diff)) %>% 
                       mutate(sum = sum(abs(`diff_Hood Canal`), abs(diff_SJI)))
                     )) %>% 
  select(phylum, suma) %>% 
  unnest(suma) %>% 
  group_by(phylum) %>% arrange(desc(sum)) %>% 
  separate(taxa, into = c("family","genus", "species"), sep = "\\|", remove = F) %>%
  mutate(label = case_when((species == "NA" & genus == "NA") ~ paste0(family, " sp."),
                           species == "NA" ~  paste0(genus, " sp."),
                           TRUE            ~ species)) -> taxa.and.diff

taxa.and.diff %>% 
  filter(str_detect(label, paste(c("Centropages", "Nitzschia lo", "Nitzschia pro","Prorocentrum", "Emili", "Alexandrium", "Chaetoceros soc","Stephanodiscus","Coscinodiscus", "Karlodi",
                                   #"Navicula cry","Navicula gla",
                                   "Chryso", "Bathy", "Gym", "Li"), collapse = "|"))) %>% select(taxa, label)-> second.sel

@@

expanded.future %>% 
  separate(taxa, into = c("family","genus", "species"), sep = "\\|", remove = F) %>%
  mutate(label = case_when((species == "NA" & genus == "NA") ~ paste0(family, " sp."),
                           species == "NA" ~  paste0(genus, " sp."),
                           TRUE            ~ species))    %>%
  mutate(Area = as.character(Area)) %>%
  mutate(Area = case_when(Area == "SJI" ~ "San Juan Island",
                          TRUE          ~ Area)) %>%
  mutate(Year = fct_rev(as.factor(Year) )) -> input.for.left

input.for.left %>%
   group_by(phylum, Temperature, pH, Year, Area ) %>%
  summarise(present = sum(present)) %>%
  group_by(phylum,Area) %>% 
  mutate(present = present/max(present)) %>% 
  mutate (label = phylum) -> phylum.stats

phylum.stats %>% 
  nest(-phylum) %>% 
  mutate( plot.by.phyl = map2 (data, phylum, ~ .x %>%
  ggplot(aes()) +
  scale_fill_brewer(name = "Year",  type = "qual", palette = 4, direction = 1,
                    breaks=c("2017","2095")) +
  labs (x = "Standardized richness",
        y = "") +
  facet_wrap(~Area) +
  theme_minimal() +
  theme (strip.text.y = element_text(angle = 0),
        axis.text.y = element_text(face = "italic"), 
        #plot.background   = element_rect(fill = "#E5E9F0"),
        legend.direction = "horizontal",
        legend.position  = "bottom",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold",vjust =  -5 ),
        axis.title.x.top  = element_text(face = "bold",vjust = 3) ) +
        geom_histogram(aes( x= present,after_stat(ncount),
                            fill = as.factor(Year),
                            group= as.factor(Year)),
                       binwidth = 0.025,
                       colour = "black",
                       position = "identity", 
                       alpha = 0.75) +
        scale_x_continuous(position = "top", limits = c(0,1)))) %>% 
  select(-data)-> summary.plot

input.for.left %>% 
  semi_join(second.sel, by = "taxa") %>%
  nest(-phylum) %>% 
  mutate( plot.by.taxa = map2 (data, phylum, ~ .x %>%
                                 ggplot(aes(x= present,
                                           y = label)) +
                                 scale_fill_brewer(name = "Year",  type = "qual", palette = 4, direction = 1,
                                                   breaks=c("2017","2095")) +
                                 labs (x = "Probability of presence",
                                       y = "") +
                                 facet_wrap(~Area) +
                                 theme_minimal() +
                                 theme(strip.text.y = element_text(angle = 0),
                                       axis.text.y = element_text(face = "italic"),
                                       legend.direction = "horizontal",
                                       legend.position  = "bottom",
                                       plot.title.position = "plot",
                                       plot.title = element_text(face = "bold",vjust =  -5 ),
                                       axis.title.x.top  = element_text(face = "bold",vjust = 3) ) +
                                 ggtitle(.y)  +
                                 geom_boxplot(aes(fill = as.factor(Year)), outlier.alpha = 0.5) +
                                 scale_x_continuous(position = "top") )) -> fig3.left

fig3.left %>%  right_join(summary.plot) -> left.plot.all
left.plot.all %>% pull(plot.by.phyl) %>% set_names(nm = left.plot.all$phylum) -> left.plot.top
left.plot.all %>% pull(plot.by.taxa) %>% set_names(nm = left.plot.all$phylum) -> left.plot

@@

  scale_color_brewer(name = "Year",  type = "qual", palette = 4, direction = -1, breaks=c("2017","2095")) +
  ggforce::geom_mark_hull(data = future.scenario %>%
                            ungroup() %>%
                            mutate(Area = as.character(Area)) %>% 
                            mutate(Area = case_when(Area == "SJI" ~ "San Juan Island",
                            TRUE          ~ Area)) %>%
                            filter (Year %in% c(2017, 2095)) ,
                          aes(x= TemperatureCelsius, y = pH_units, group= Year, color = as.factor(Year),label = as.factor(Year)),
                          expand = unit(0.5, "mm"),
                 label.margin = margin(1, 1, 1, 1, "mm"),
                 label.buffer = unit(0, "mm"),
                 con.cap = 0 ,
                 alpha = 0.5) +
     facet_grid(.~Area, scales = "free_x",space = "free_x") +
  guides(color = "none") +
    labs (x = "Temperature",
          y= "pH") +
    theme_minimal()+
    theme(legend.position = "bottom",
          legend.key.width  = unit(2 ,"cm"),
          axis.title.x = element_text(face = "bold"),
          legend.direction = "horizontal") +
    scale_x_continuous(position = "top")
}
```

@@

@@

Following reviewer's suggestions, we are limiting the information displayed in the main Figures to two of most important phyla for coastal ecosystems dinamics: Diatoms and Dinoflagellates.
```{r}
layout <- "
AA
BB
##
CC
DD
##
EE
GG
HH
"
wrap_plots(A = left.plot[["Dinophyceae"]] + labs(title = "A.1", tag = "Dinophyceae") ,
           B = left.plot.top[["Dinophyceae"]] + guides(fill = "none")+ labs(title  ="A.2"),
          # F = plot_spacer(),
           C = left.plot[["Bacillariophyta"]] + labs(title ="B.1", tag = "Bacillariophyta"),
           D = left.plot.top[["Bacillariophyta"]] + guides(fill = "none")+ labs(title ="B.2"),
           E = left.plot[["Haptophyceae"]] + labs(title ="C.1", tag = "Haptophyceae"),
           G = left.plot.top[["Haptophyceae"]] + guides(fill = "none")+ labs(title  ="C.2"),
           H = guide_area(), design = layout, heights = c(3,2,1,3,2,1,3,2,1), guides = "collect") &
  theme(plot.tag.position = c(0.1,1),
        plot.tag = element_text(face = "bold")) -> left

layout2 <- "
AA
AA
##
CC
CC
##
EE
EE
HH
"
wrap_plots(A = fig3.right[["Dinophyceae"]] + labs(title  ="A.3"),
          # F = plot_spacer(),
           C = fig3.right[["Bacillariophyta"]] + labs(title ="B.3"),
           E = fig3.right[["Haptophyceae"]]+ labs(title ="C.3"),
           H = guide_area(), design = layout2, heights = c(3,2,1,3,2,1,3,2,1), guides = "collect")&
  theme(plot.tag.position = c(0.1,1),
        plot.title  = element_text(face = "bold")) -> right

(left|right)+plot_layout(widths = c(2,2))  -> plot 
   ggsave(plot , filename = here("Figures","Manuscript", paste0("Top_fig3_",Sys.Date(),".Other.sel.png")), units = "in", dpi = "retina", width = 20, height = 14)

@@

```{r}
input.for.left %>% 
  nest(-phylum) %>% 
  mutate( plot.by.taxa = map2 (data, phylum, ~ .x %>%
                                 ggplot(aes(x= present,
                                           y = label)) +
                                 scale_fill_brewer(name = "Year",  type = "qual", palette = 4, direction = 1,
                                                   breaks=c("2017","2095")) +
                                 labs (x = "Probability of presence",
                                       y = "") +
                                 facet_wrap(~Area) +
                                 theme_minimal() +
                                 theme(strip.text.y = element_text(angle = 0),
                                       axis.text.y = element_text(face = "italic"),
                                       legend.direction = "horizontal",
                                       legend.position  = "bottom",
                                       plot.title.position = "plot",
                                       plot.title = element_text(face = "bold",vjust =  -5 ),
                                       axis.title.x.top  = element_text(face = "bold",vjust = 3) ) +
                                 ggtitle(.y)  +
                                 geom_boxplot(aes(fill = as.factor(Year)), outlier.alpha = 0.5) +
                                 scale_x_continuous(position = "top") )) -> fig3.left

fig3.left %>% 
  left_join(list.of.richness.plots, by = "phylum") -> fig3.left

fig3.left %>% pull(plot) %>% set_names(fig3.left$phylum) -> rights
fig3.left %>% pull(plot.by.taxa) %>% set_names(fig3.left$phylum) -> lefts

map2(lefts, rights, 
     function(.x,.y){

@@

paths <- paste0("Supp.fig.",names(lefts),".png")
